TacticToe: Learning the Game of Tactics

### 2018-01-20 tactictoe_jv.tex
removing old experiment

@@

\subsection{Preselecting feature vectors and their  
dependencies}\label{sec:dependencies}
We first rank feature vectors by their distance to the conjecture. But better 
ranked vectors only contains symbols from 
the conjecture and may not be suitable for later stages of the proof where the 
goals may have derived significantly from the conjecture. To solve this 
problem, we reorder the list so that descendants (see 
Definition~\ref{def:descendant}) of vectors inherits the similarity of their 
parent.

\begin{definition}(Descendant of a feature vector)\label{def:descendant}
Let $\mathfrak{F}$ be a set of recorded feature vectors. 
The set of all descendants $D_\infty$ of a feature vector $f$ is 
inductively defined by:

@@

We augment the ordered predictions by inserting after each predicted vector 
its descendants and removing lower ranked duplicates. This contrast with 
theorem predictions where we only select parents. This phase is only applied 
during preselection, so is of no great consequence as long as we select enough 
theorems and tactics.

>>>>

\todo{include latest results: 66.56 percent of 7123 theorems in 60 seconds and
do a similar experiment for hh with minimization}

@@

\subsection{Preselecting feature vectors and their  
recursive dependencies}\label{sec:dependencies}
We first rank feature vectors by their distance to the conjecture. But better 
ranked vectors only contains symbols from 
the conjecture and may not be suitable for later stages of the proof where the 
goals may have derived significantly from the conjecture. To solve this 
problem, we reorder the list so that descendants (see 
Definition~\ref{def:recdep}) of vectors inherits the similarity of their 
parent.

\begin{definition}(Recursive dependencies of a feature 
vector)\label{def:recdep}
Let $\mathfrak{F}$ be a set of recorded feature vectors. 
The set of all recursive dependencies $D_\infty$ of a feature vector $f$ is 
inductively defined by:

@@

We augment the ordered predictions by inserting after each predicted vector 
its descendants and removing lower ranked duplicates. 
%This contrast with 
%theorem predictions where we only select parents. 
 This phase is only applied 
during preselection, so is of no great consequence as long as we select enough 
theorems and tactics.
